Imposing a Weight Norm Constraint for Neuro-Adaptive Control

### 2025-06-07 presentation/presentation.tex
minor update

% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro–Adaptive Control 
} 
\subtitle{
    \textit{IEEE European Control Conference (ECC) 2025}\\
}
\author{Myeongseok Ryu\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}}
\date{\today}
% \institute[short]{\inst{1} First \samelineand \inst{2} Second \samelineand \inst{3} Third}
\newcommand{\samelineand}{\\}
\institute{%
    \begin{minipage}[c]{\linewidth}
        \centering
        \inst{1}%
        Department of Mechanical and Robotics Engineering\\
        Gwangju Institute of Science and Technology
        \and
        \inst{2}%
        AI Graduate School\\
        Gwangju Institute of Science and Technology
  \end{minipage}
}
% make institute font size smaller
\setbeamerfont{institute}{size=\normalsize}

\logo{
  \vspace{-.7cm}%
  \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.jpg}
  \includegraphics[height=0.3cm]{assets/kaist_logo.png}
  \hspace{.6cm}%
  }

@@

\subsection{Introduction to Neuro–Adaptive Control}

\begin{frame}{\insertsubsectionhead}{What is Neuro–Adaptive Control?}

  \textbf{Neuro–Adaptive Control}
  \small{
    \begin{itemize}
      \item \textbf{Neuro–adaptive control} (NAC) is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control techniques} \cite{Farrell:2006aa}.
      \item It is used to handle \textbf{uncertainties} and \textbf{nonlinearity} in dynamic systems. 
    \end{itemize}
  }

  \begin{figure}
    \includegraphics[width=0.55\textwidth]{figures/NAC.drawio.pdf}
  \end{figure}

@@

\begin{frame}{\insertsubsectionhead}{What is Neuro–Adaptive Control?}

  \textbf{Advantages of Neuro-Adaptive Control}
  \small{
    \begin{itemize}
      \item \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
      \item \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textbf{Lyapunov stability theory}.
      \item \textbf{Online Learning Capability}: NAC adapts in \textbf{real-time} to new data with stability guarantees.
      \item \textbf{Robustness}: NAC handles \textbf{uncertainties and disturbances} effectively with adaptive control techniques.
    \end{itemize}
  }

@@

  \textbf{Challenges}
  \small{
    \begin{itemize}
      \item \textbf{Optimality}: In general, the adaptation laws are driven with respect to the tracking error, which may not guarantee optimal performance.
      \item \textbf{Unpredictable Amplitude of NN Weights}: 
        \begin{itemize}
          \item NN weights may diverge, leading to instability.
          \item This can result in unpredictable behavior of the controller.
        \end{itemize}
      \item \textbf{Parameter Dependency}: 
    \end{itemize}
  }

@@

>>>>

% Title page details: 
\title{
    Imposing a Weight Norm Constraint for Neuro-Adaptive Control 
} 
\subtitle{
    \textit{IEEE European Control Conference (ECC) 2025}\\
}
\author{
  \textbf{Myeongseok Ryu}\inst{1}, Jiyun Kim\inst{2}, and Kyunghwan Choi\inst{1}
  }
\date{\today}
% \institute[short]{\inst{1} First \samelineand \inst{2} Second \samelineand \inst{3} Third}
\newcommand{\samelineand}{\\}
\institute{%
    \begin{minipage}[c]{\linewidth}
        \centering
        \inst{1}%
        Department of Mechanical and Robotics Engineering\\
        Gwangju Institute of Science and Technology
        \and
        \inst{2}%
        AI Graduate School\\
        Gwangju Institute of Science and Technology
  \end{minipage}
}
% make institute font size smaller
\setbeamerfont{institute}{size=\normalsize}

\logo{
  \vspace{-.7cm}%
  \includegraphics[height=0.3cm]{assets/kaist_logo.png}
  \includegraphics[height=0.3cm]{assets/MIC_Lab_logo.jpg}
  \hspace{.6cm}%
  }

@@

\subsection{Introduction to Neuro-Adaptive Control}

\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}

  \textbf{Neuro-Adaptive Control}
  \small{
    \begin{itemize}
      \item \textbf{Neuro-adaptive control} (NAC) is a control strategy that combines \textbf{neural networks (NNs)} with \textbf{adaptive control} \cite{Farrell:2006aa}.
      \item Features of both \textbf{NNs} and \textbf{adaptive control} can be found in NAC.
    \end{itemize}
  }

  \begin{figure}
    \includegraphics[width=0.65\textwidth]{figures/NAC.drawio.pdf}
  \end{figure}

@@

\begin{frame}{\insertsubsectionhead}{What is Neuro-Adaptive Control?}

  \textbf{Advantages of Neuro-Adaptive Control}
  \small{
    \begin{itemize}
      \item \textbf{Adaptability}: NAC adapts to changing environments and system dynamics.
      \item \textbf{Stability Guarantee}: The closed-loop stability is ensured using \textit{Lyapunov stability theory}.
      \item \textbf{Online Learning Capability}: NAC adapts in \textit{real-time} to new data with stability guarantees.
      \item \textbf{Robustness}: NAC handles \textit{uncertainties and disturbances} effectively with adaptive control techniques.
    \end{itemize}
  }

@@

  \textbf{Challenges}
  \small{
    \begin{itemize}
      \item \textbf{Optimality}: In general, the adaptation laws are driven with respect to the tracking error, which may not guarantee optimal performance.
      \item \textbf{Unpredictable Amplitude of Control input}: 
        \begin{itemize}
          \item The maximum amplitude of the NN weights is not predictable.
          \item This can result in unpredictable amplitude of the control input, which may lead to control saturation.
        \end{itemize}
      \item \textbf{Parameter Dependency}: 
      \begin{itemize}
        \item The performance of the NAC is highly dependent on the choice of parameters, such as learning rate and NN architecture.
      \end{itemize}
    \end{itemize}
  }

@@

  \begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/exp_set.drawio.png}
    \caption{2-Link Robotic Manipulator}
  \end{figure}

  \let\thefootnote\relax\footnote{
    \textit{Notations}: 
      $\mv{q}$: Joint position, $\mv{\dot{q}}$: Joint velocity, $\mv{\tau}$: Control input, $\mm{M}$: Inertia matrix, $\mm{C}$: Coriolis matrix, $\mm{G}$: Gravity vector.
  }
